---
title: "FARS package vignette"
author: "Dunja Kurtoic"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a package for analysing U.S. National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS) data. The built-in functions provide loading the data, summarizing it and plotting.

```{r}
library(fars)
```

```{r, echo=F}
make_filename <- function(year) {
  year <- as.integer(year)
  sprintf("accident_%d.csv.bz2", year)
}
```

* This package contains five functions:
 + fars_read() - to load your data.
 + make_filename() - to automatically create a file name, you just pass the year.
```{r} 
make_filename(2013)
```
 
 + fars_read_years() - reads files according to the years you submit.
 + fars_summarize_years() - summarizes data per year
 + fars_map_state() - plots a map of USA according to the state number you pass. Each dot represents a crime in given time.

