---
title: "FARS package vignette"
author: "Dunja Kurtoic"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a package for analysing U.S. National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS) data. The built-in functions provide loading the data, summarizing it and plotting.

```{r}
#library(fars)
```

```{r, echo=F}
make_filename <- function(year) {
  year <- as.integer(year)
  sprintf("accident_%d.csv.bz2", year)
}
```

* This package contains five functions:
 + fars_read() - to load your data.
 + make_filename() - to automatically create a file name, you just pass the year.
```{r} 
make_filename(2013)
```
 
 + fars_read_years() - reads files according to the years you submit.

```{r,include=F}
library("dplyr")
library("readr")
fars_summarize_years <- function(years) {
  MONTH=NULL
  year=NULL

  if(getRversion() >= "2.15.1")  utils::globalVariables("MONTH")
  #dat_list <- fars_read_years(years)
  dat_list <- read_csv("~/Documents/coursera_MasteringSDinR/fars/inst/extdata/accident_2013.csv.bz2", progress = FALSE)
  dat_list2 <- dplyr::bind_rows(dat_list)
    dat_list2 %>% dplyr::group_by_(~YEAR, ~MONTH) %>%
    dplyr::summarize_(n = ~n()) %>%
    tidyr::spread_(key_col = "YEAR", value_col = "n")
}
```
 + fars_summarize_years() - summarizes data per year
 
```{r, include=F}
var <- fars_summarize_years(2013)
```
`fars_summarize_years(2013)`
```{r,echo=F}
var
```
 + fars_map_state() - plots a map of USA according to the state number you pass. Each dot represents a crime in given time.

